Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
removed some todos, responded to others

%Some readers might know that there are four blame strategies: $ \{Lazy, 
%Eager\} 
%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
%potential type errors, but 
%blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. 
\todo[inline]{Why do we need to explain why both LD and LUD? -KC}

@@

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax in \citet{siek2009exploring} with sum 
types and product types. Besides, we annotate function codomain explicitly 
because we need to compute identity hypercoercion for the codomain when 
evaluating cast calculus with hypercoercions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -JS
\\ --- \\ Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -JS
\\ --- \\ Fixed -KC}
\todo[inline]{Why do you annotate the codomain of lambda abstractions
	explicitly? -JS
	\\---\\
	Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC
        \\---\\
        The answer you put in the text is too vague. -JS
        \\---\\
        Fixed. -KC}
Let $ T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

$ T_1 \sim T_2 $ reads ``$ T_1 $ and $ T_2 $ are consistent''.
The intuition of $ T_1 \sim T_2 $ is that $ T_1 $ and $ T_2 $ have no conflict 
type information. Two types are consistent if one of them is $ \star $, or they 
have the same top-most type constructor and the corresponding sub-parts are 
consistent. Consistency is reflexive and symmetric, but not transitive.

$ T_1 \smile T_2 $ reads ``$ T_1 $ and $ T_2 $ are shallowly-consistent''. Two 
types are shallowly consistent if one of them is $ \star $, or they have the 
same type constructor at the top. Shallow-inconsistency is the root of all 
blame in lazy cast strategies -- casting a value to a shallowly inconsistent 
type leads to a blame. Shallow-consistency is reflexive, symmetric, but 
not transitive.

Let $ e $ range over terms. Most terms are standard. We annotate the codomain 
of lambda abstractions explicitly because we need it when evaluating cast 
calculus with hypercoercion. We have two additional terms: cast expressions and 
blame expressions. Cast expressions insert runtime type checks. And blame 
expressions raise an error. The typing rules for the additional terms are
straightforward.

@@

Fig.~\ref{machine-cekc} defines the dynamic semantics of cast calculi as a 
CEK machine \citep{felleisen1986control}. CEK machines include continuation as 
part of their states. They evaluate expressions with two interleaving 
processes: 
(1) dive into an expression and extend the continuation;
(2) return a value to the current continuation.
\todo[inline]{Briefly present the main ideas regarding how a CEK
	machine works. (2-3 sentences) -JS
\\---\\Fixed -KC}

Most existing proofs about cast calculi defines the dynamic semantics with 
reduction semantics. We use a CEK machine instead because the first author is 
more familiar with CEK machines, and that he believes CEK machines are more 
convenient because space-efficiency is about compressing continuations.
\todo[inline]{Explain why you are using a CEK machine instead of
	reduction semantics. -JS
        \\---\\Fixed -KC
        \\---\\
        Change ``one of us'' to ``first author''. -JS
 		\\---\\Fixed -KC
}

\todo[inline]{Please fill in the missing reduction rules. -JS
\\---\\ Fixed -KC}
\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -JS
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC
	\\---\\
    It's better because it matches the postfix syntax we are using for
    casts. Currently line 2 of applyCast for D is difficult to read,
    compare it with line 4 of applyCast for UD. -JS
    \\---\\
    Does it mean changing the syntax for casts to a prefix syntax would work as 
    well? 
    If yes, I prefer this way, because of the reason in my first response 
    and that function applications (apply) also takes arguments in this order.
    I have fixed it with my idea so that we can see if it works. This change is 
    easy to undo.
    -KC
    }

@@

\todo[inline]{What is the main idea behind the organization of
 hypercoercions? -JS
 \\---\\
 Are you asking why hc has three parts? Or why these subsections 
in this section? -KC}

@@

\todo[inline]{Give a high-level summary of the proof.
	The summary should be enough so that the reader knows a bit
	about why you introduce the various definitions below. -JS
\\---\\
Fixed -KC}

@@

\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
	$ \mathcal{C} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{} and is a monoid,
	\[
	\judgeSeval{C}{e}{o}
	 \; \text{if and only if} \; 
	\judgeDeval{e}{o}
	\]
\end{lemma}
\begin{proof}Proving left implies right is trivial.
To prove $ \judgeDeval{e}{o} $ implies $ \judgeSeval{C}{e}{o} $, 
we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
taking one or more steps in \ineffCEKD. As we just took a positive number of 
steps, we are closer to the halting state.
	\todo[inline]{I'm guessing that you prove this lemma by induction,
		using Lemma~\ref{thm:surely-monoidic-reduce}.
		Proofs by induction are not ``immediate''. -JS
	\\---\\Fixed. -KC}
\end{proof}

>>>>

%Some readers might know that there are four blame strategies: $ \{Lazy, 
%Eager\} 
%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
%potential type errors, but 
%blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. 
\todo[inline]{Why do we need to explain why both LD and LUD? -KC
  \\---\\
Because the paper includes both. -JS}

@@

\figref{fig:blame-static} defines the syntax of cast calculi and its
static semantics. We extend the syntax of \citet{siek2009exploring}
with sum and product types.  Let $ T $ range over types. A type is
either the dynamic type $ \star $ (a.k.a. $ \mathtt{Dyn} $, $
\mathbb{?} $, or $ \mathtt{Unknown} $), or a type with a type
constructor at the top, that is, a pre-type, ranged over by $ P $. We
include just one base type, $\POOunit$. The other pre-types are
functions, products, and sums.

As usual we write $ T_1 \sim T_2 $ when $ T_1 $ and $ T_2 $ are
consistent. The intuition of $ T_1 \sim T_2 $ is that $ T_1 $ and $
T_2 $ have no conflicting type information. Two types are consistent
if one of them is $ \star $, or they have the same top-most type
constructor and the corresponding sub-parts are
consistent. Consistency is reflexive and symmetric, but not
transitive.

We write $ T_1 \smile T_2 $ when $ T_1 $ and $ T_2 $ are
shallowly-consistent, that is, if one of them is $ \star $, or they
have the same type constructor at the top. Shallow-inconsistency is
the root of all blame in lazy cast strategies -- casting a value to a
shallowly inconsistent type leads to a blame. Shallow-consistency is
reflexive, symmetric, but not transitive.

Let $ e $ range over terms. Most terms are standard for a simply-typed
lambda calculus. We annotate the codomain of a lambda abstraction
explicitly because we refer to it in the dynamic semantics. Becuase
this is a cast calculus, we have two additional terms: cast
expressions and blame expressions. Cast expressions perform runtime
type checks and blame expressions raise an error.

@@

Fig.~\ref{machine-cekc} defines the dynamic semantics of cast calculi as a 
CEK machine \citep{felleisen1986control}. CEK machines include continuation as 
part of their states. They evaluate expressions with two interleaving 
processes: 
(1) dive into an expression and extend the continuation;
(2) return a value to the current continuation.

Most existing proofs about cast calculi defines the dynamic semantics with 
reduction semantics. We use a CEK machine instead because the first author is 
more familiar with CEK machines, and that he believes CEK machines are more 
convenient because space-efficiency is about compressing continuations.

\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -JS
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC
	\\---\\
    It's better because it matches the postfix syntax we are using for
    casts. Currently line 2 of applyCast for D is difficult to read,
    compare it with line 4 of applyCast for UD. -JS
    \\---\\
    Does it mean changing the syntax for casts to a prefix syntax would work as 
    well? 
    If yes, I prefer this way, because of the reason in my first response 
    and that function applications (apply) also takes arguments in this order.
    I have fixed it with my idea so that we can see if it works. This change is 
    easy to undo.
    -KC
    \\---\\
    Postfix is better than prefix because then the casts read left to right,
    which is the normal direction for English readers.
    Please make it so. -JS
    }

@@

\todo[inline]{What is the main idea behind the organization of
 hypercoercions? -JS
 \\---\\
 Are you asking why hc has three parts? Or why these subsections 
 in this section? -KC
 \\---\\
 three parts -JS
}

@@

@@

\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
	$ \mathcal{C} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{} and is a monoid,
	\[
	\judgeSeval{C}{e}{o}
	 \; \text{if and only if} \; 
	\judgeDeval{e}{o}
	\]
\end{lemma}
\begin{proof}Proving left implies right is trivial.
To prove $ \judgeDeval{e}{o} $ implies $ \judgeSeval{C}{e}{o} $, 
we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
taking one or more steps in \ineffCEKD. As we just took a positive number of 
steps, we are closer to the halting state.
\end{proof}
